Self Regulation Ontology Retest Data Report

### 2017-03-22 SRO_Report.Rmd
working on report

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(lavaan)
library(semTools)
library(psych)
library(GPArotation)
library(rmarkdown)
library(psych)
library(stringr)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', html_notebook(toc = T, toc_float = T))}
```

@@

Distribution of Spearman correlations
```{r warning=FALSE, message=FALSE}
cor_df %>%
  ggplot(aes(spearman))+
  geom_histogram()+
  theme_bw()+
  ggtitle('Distribution of Spearman correlations for cleaned meaningful variables')
```

@@

Spearman correlations for surveys are noticably higher than task reliabilities.
```{r warning=FALSE, message=FALSE}
cor_df %>%
  ggplot(aes(spearman))+
  geom_histogram()+
  theme_bw()+
  facet_wrap(~task)
```

@@

Survey reliabilities are noticably higher than task reliabilities.
```{r warning=FALSE, message=FALSE, fig.width=10}
icc_df %>%
  gather(key,value,-dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(position = 'stack', alpha=0.5)+
  theme_bw()+
  facet_wrap(~key,scales='free')
```

@@

```{r}
icc_df %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  ggplot(aes(spearman, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank())
```

@@

```{r}
icc_df %>%
  ggplot(aes(eta_sq, icc, col=task))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank())
```

>>>>

```{r, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(gridExtra)
library(lme4)
library(GGally)
library(jsonlite)
library(psych)
library(rmarkdown)
library(psych)
library(stringr)
library(plotly)
sem <- function(x) {sd(x, na.rm=T) / sqrt(length(x))}
render_this <- function(){rmarkdown::render('SRO_Report.Rmd', output_dir = '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Report', html_notebook(toc = T, toc_float = T))}
```

@@

@@

Spearman correlations for surveys are noticably higher than task reliabilities.
```{r warning=FALSE, message=FALSE}
ggplotly(cor_df %>%
  ggplot(aes(spearman, fill=task, label=dv))+
  geom_histogram(alpha=0.5, position='identity')+
  theme_bw()+
  theme(legend.title = element_blank()))
```

@@

Survey reliabilities are noticably higher than task reliabilities.
```{r warning=FALSE, message=FALSE, fig.width=10}
icc_df %>%
  gather(key,value,-dv, -task) %>%
  ggplot(aes(value, fill=task))+
  geom_histogram(position = 'identity', alpha=0.5)+
  theme_bw()+
  facet_wrap(~key,scales='free')
```

@@

```{r}
ggplotly(icc_df %>%
           left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
           ggplot(aes(spearman, icc, col=task, label=dv, label2=eta_sq))+
           geom_point()+
           theme_bw()+
           theme(legend.title = element_blank())+
           geom_abline(intercept = 0, slope=1))
```

@@

```{r}
ggplotly(icc_df %>%
  ggplot(aes(eta_sq, icc, col=task, label=dv))+
  geom_point()+
  theme_bw()+
  theme(legend.title = element_blank()))
```
